---
title: "Coding Challenge 4: Markdown"
author: "Zachary Noel"
date: "2025-02-24"
output:
  html_document:
    toc: true
  word_document:
    toc: true
  md_document: 
    variant: gfm
---

# Coding Challenge 4

## Question 1 
a. A YAML header is ... 
b. A pull request is when ... 
c. literate programming is when ... 

## Question 2: Coding challenge 2 in .r markdown format

Here, we will analyze mycotoxin data collected from wheat heads grown in the greenhouse inoculated with Fusarium graminearum (Fg) with or without fungal endophytes to protect against Fg. The experiment was performed by inoculating the heads with Fg (positive control), Fg + 1 of 3 endophytes (Fg + 40, Fg + 70, or Fg + 37), and the non-treated control (NTC). Therefore, the experiment was five treatments with 6-10 technical replicates and three experimental replicates. The authors quantified the parts per million (ppm) of mycotoxins Deoxynivalenol (DON) and the variant 15ADON from the wheat grain, and this is your primary response variable. In other words, we are interested in knowing if the fungal endophytes could reduce the concentration of DON on wheat heads. This was done across two wheat cultivars, a winter wheat variety, Ambassador, and a spring wheat variety, Wheaton. These data are published here: 

Load in the library you will need
```{r}
library(ggplot2)
library(ggpubr)
```

Colorblind pallet needed 
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

### Question 2a - clickable link to manuscript where data are published

- Noel, Z.A., Roze, L.V., Breunig, M., Trail, F. 2022. Endophytic fungi as promising biocontrol agent to protect wheat from Fusarium graminearum head blight. Plant Disease. <https://doi.org/10.1094/PDIS-06-21-1253-RE>
- The following github repository is associated with this paper: <https://github.com/noelzach/EndophyteBiocontrol>

### Question 2b - Read in the data using a relative file path
```{r}
DON_data <- read.csv("CodingChallenge4/MycotoxinData.csv", na.strings = "na")
```

### Question 2c - Last question of Coding challenge 3

#### DON figure
```{r, echo=F, eval=F}
# DON
DON_plot <- ggplot(DON_data, aes(x = Treatment, y = DON, fill = Cultivar)) +
  geom_boxplot(outliers = T, outlier.shape = 15) +
  ylab("DON (ppm)") +
  xlab("") +
  geom_jitter(pch = 21, position = position_jitterdodge(), color = "black", alpha = 0.6) + 
  scale_fill_manual(values = c(cbbPalette[[3]], cbbPalette[[4]])) +
  theme_classic() +
  facet_wrap(~Cultivar)
DON_plot

stats_donplot <- DON_plot + 
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}", p.adjust.method = "fdr")
```

#### 15A DON
```{r, echo=F, eval=F}
DON_15 <- ggplot(DON_data, aes(x = Treatment, y = X15ADON, fill = Cultivar)) +
  geom_boxplot(outliers = F) +
  ylab("DON (ppm)") +
  xlab("") +
  geom_jitter(pch = 21, position = position_jitterdodge(), color = "black") + 
  scale_fill_manual(values = c(cbbPalette[[3]], cbbPalette[[4]])) +
  theme_classic() +
  facet_wrap(~Cultivar)
DON_15

stats_DON_15 <- DON_15 + 
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}", p.adjust.method = "fdr")
```

#### Seedmass
```{r, echo=F, eval=F}
seedmass <- ggplot(DON_data, aes(x = Treatment, y = MassperSeed_mg, fill = Cultivar)) +
  geom_boxplot(outliers = F) +
  ylab("DON (ppm)") +
  xlab("") +
  geom_jitter(pch = 21, position = position_jitterdodge(), color = "black") + 
  scale_fill_manual(values = c(cbbPalette[[3]], cbbPalette[[4]])) +
  theme_classic() +
  facet_wrap(~Cultivar)
seedmass

stats_seedmass <- seedmass + 
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}", p.adjust.method = "fdr")
```

#### Combine them all togetether
```{r, echo=F, eval=F}
ggarrange(stats_donplot, stats_DON_15, stats_seedmass, labels = "auto", ncol = 3, nrow = 1, common.legend = T)
```

## Question 3

A table of contents was created by changing ... , and can be viewed in the rendered docx or pdf document.

## Question 4

A directory was created inside my top level directory called coding challenge 4 for my repository and I put the .md and .docx files there. 

## Question 5

I edited the readme of my repository to make a clickable link to the .md file so it was viewable on github. 

## Question 6 

This is a link to my GitHub
<https://github.com/noelzach/Dummy>




